Staged Abstract Interpreters

### 2019-03-08 paper/10_intro.tex
misc

Our second contribution is to enable modular analysis based on a whole-program
analyzer by meta-programming. Modern software are shipped with large libraries
\cite{toman_et_al:LIPIcs:2017:7121}, and analyzing programs with large libraries
is usually expensive or unnecessarily repeated for whole-program analyzing
algorithms. For example, it has been shown that analyzing a simple ``Hello
World'' program in Java depends on additional 3,000 classes in the library
\cite{DBLP:conf/oopsla/KulkarniMZN16}. Meta-programming gives us a chance to
tweak a whole-program analyzing algorithm into an analyzer that can work on
different components of program separately. Still, the idea is to specialize the
abstract interpreter used for whole-program analysis, but on a subset of the
program, for examples, several generic functions for list manipulation. Such
specialization works on a lambda expression and generates code, which is partial
analysis results and can be completed by running with the necessary arguments
(for example, an environment that closes the lambda term) at next stages. Multiple
partial analysis results also can be reused later and composed together as they
are just normal programs at the next stage. Through staging, we mechanically
obtain a modular analysis, even though the original algorithm is formulated as a
whole-program analysis.

@@

\note{
  Expression problem \cite{DBLP:conf/icfp/GibbonsW14, DBLP:conf/ecoop/KrishnamurthiFF98, expproblem},
}

>>>>

Our second contribution is to enable modular analysis based on a whole-program
analyzer by meta-programming. Modern software are shipped with large libraries
\cite{toman_et_al:LIPIcs:2017:7121}, and analyzing programs with large libraries
is usually expensive or unnecessarily repeated for whole-program analyzing
algorithms. For example, it has been shown that analyzing a simple ``Hello
World'' program in Java depends on additional 3,000 classes in the library
\cite{DBLP:conf/oopsla/KulkarniMZN16}. A natural idea is to analyze libraries
and generate summaries, later we can plugin the necessary information into the
summaries and finish the analysis; therefore such summaries should be modular
and reusable. Meta-programming gives us a chance to readily tweak a
whole-program analyzing algorithm into an analyzer that works modularly and
produces summaries. Still, the idea is to specialize the abstract interpreter
that was used for whole-program analysis, but on a subset of the program, for
examples, several generic functions for list manipulation. Such specialization
works on lambda expressions and generates code, which is partial analysis
results and can be completed by running with the necessary arguments (for
example, an environment that closes the lambda term) at next stages. Multiple
partial analysis results also can be reused later and composed together as they
are just normal programs at the next stage. Through staging, we mechanically
obtain a modular analysis, even though the original algorithm is formulated as a
whole-program analysis.

@@

%\note{Expression problem \cite{DBLP:conf/icfp/GibbonsW14, DBLP:conf/ecoop/KrishnamurthiFF98, expproblem},}
